### 2020-06-14 manuscript/PLOS-MSc-Thesis.tex
change title

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Gene regulatory networks producing a striped band of gene 
expression} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1\Yinyang},
Gloria Machado-Rodríguez\textsuperscript{1\Yinyang},
Boris Rodríguez-Rey\textsuperscript{2\textcurrency},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Instituto de Biología, Universidad de Antioquia, Medellín,
Antioquia, Colombia
\\
\textbf{2} Instituto de Física, Universidad de Antioquia, Medellín, Antioquia,
Colombia
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

>>>>

%\newcommand{\lorem}{{\bf LOREM}}
%\newcommand{\ipsum}{{\bf IPSUM}}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory 
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1\Yinyang},
Gloria Machado-Rodríguez\textsuperscript{1\Yinyang},
Boris Rodríguez-Rey\textsuperscript{2\textcurrency},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Instituto de Biología, Universidad de Antioquia, Medellín,
Antioquia, Colombia
\\
\textbf{2} Instituto de Física, Universidad de Antioquia, Medellín, Antioquia,
Colombia
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip
